Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-05-08 main.Rmd
structural changes to Section 3. Merging Section 4 to Section 3

@@

# Relativities {#sec:cyclic-calendar}

@@

The cyclic calendar algebra consists of broadly two kinds of operations:
(1) **single-to-multiple** and (2) **multiple-to-single** \todo[inline]{these don't make sense to me, they are just the reverse of each other, so why are both needed. its not  clear from the  next block of text what each operation does} which entails the representation of _multiple-order-up_ cyclic granularities from _single-order-up_ cyclic granularities respectively. The hierarchical structure of time creates a natural nested ordering which can produce single-order-up or multiple-order-up granularities. We shall use the notion of a hierarchy table and order to define them.

\begin{definition}\label{def:order}
The {\bf order} of a linear granularity is the level of coarseness associated with a linear granularity. For example, for two linear granularities $G$ and $H$, if $G$ {\em groups into} or {\em finer than} $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$. In any hierarchy table, linear granularities are arranged from lowest to highest order.
\end{definition}

\begin{definition}\label{def:hierarchy} 
Let $H_n: (G, C, K)$ be a {\bf hierarchy table} containing $n$ linear granularities. $G_{l}$ and $G_{m}$ represent the linear granularity of order $l$ and $m$ respectively with $l<m$. $K \equiv P(l,m)$ represents the period length of the grouping $(G_{l}, G_{m})$ for a circular granularity and $K \equiv k(l,m)$ represents the operation to obtain $G_{m}$ from $G_{l}$ for a quasi-circular granularity $C_{G(l),G(m)}$, $\forall l,m \in {1, 2, \dots,n}$. We assume that the cyclic granularity $C_{G(l),G(m)}$ is either circular or quasi-circular. It is difficult to position an aperiodic linear granularity in a hierarchy and hence the possibility of an aperiodic cyclic granularity is not considered.
\end{definition}

We refer to granularities which are nested within multiple levels of the hierarchy table as _multiple-order-up_ and those concerning a single level as _single-order-up_ granularities.

@@

## Single-to-multiple {#sec:single-to-multiple}

### All circular single order-up granularities {#sec:all-circular}

@@

### Circular or quasi-circular single order-up granularities {#sec:notall-circular}

@@

## Multiple-to-single {#sec:multiple-to-single}

### Multiple order-up circular granularities {#sec:all-circular-multiple}

@@

### Muliple order-up quasi-circular granularities {#sec:quasi-circular-multiple}

>>>>

\begin{definition}\label{def:order}
The {\bf order} of a linear granularity is the level of coarseness associated with a linear granularity. For example, for two linear granularities $G$ and $H$, if $G$ {\em groups into} or {\em finer than} $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$.
\end{definition}

@@

## Relativities {#sec:cyclic-calendar}

@@

The hierarchical structure of time creates a natural nested ordering which can produce multiple-order-up granularities. We shall use the notion of a hierarchy table to define them.

\begin{definition}\label{def:hierarchy} 
A {\bf hierarchy table} helps to define cyclic granularities relative to linear granularities. The hierarchy table $H_n: (G, C, K)$ arranges $n$ linear granularities from lowest to higher oder and lays down the way they relate through $K$. Let $G_{l}$ and $G_{m}$ represent the linear granularity of order $l$ and $m$ respectively with $l<m$. Then $K \equiv P(l,m)$ represents the period length of the grouping $(G_{l}, G_{m})$ for a circular granularity and $K \equiv k(l,m)$ represents the operation to obtain $G_{m}$ from $G_{l}$ for a quasi-circular granularity $C_{G(l),G(m)}$, $\forall l,m \in {1, 2, \dots,n}$. 
\end{definition}

\noindent We assume that the cyclic granularity $C_{G(l),G(m)}$ is either circular or quasi-circular. It is difficult to position an aperiodic linear granularity in a hierarchy and hence the possibility of an aperiodic cyclic granularity is not considered.

\begin{definition}\label{def:norderup} 
Cyclic granularities which are nested within multiple levels of the hierarchy table are called {\bf multiple-order-up} granularities.
\end{definition}

<!-- \begin{definition}\label{def:norderup}  -->

<!-- \end{definition} -->

A _single-order-up_ is a cyclic granularity which is nested within a single level. It is a special case of multiple-order-up granularity.

## Computation through cyclic calendar algebra

The cyclic calendar algebra consists of broadly two kinds of operations:
(1) **single-to-multiple** and (2) **multiple-to-single** which entails the representation of _multiple-order-up_ cyclic granularities from _single-order-up_ cyclic granularities respectively.

@@

### Single-to-multiple {#sec:single-to-multiple}

#### All circular single order-up granularities {#sec:all-circular}

@@

#### Circular or quasi-circular single order-up granularities {#sec:notall-circular}

@@

### Multiple-to-single {#sec:multiple-to-single}

#### Multiple order-up circular granularities {#sec:all-circular-multiple}

@@

#### Muliple order-up quasi-circular granularities {#sec:quasi-circular-multiple}
